---
title: "Alcohol vs Seat choice"
author: "Tattiana Rinkenberger"
date: "06/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

```{r}
boxplot(alcohol~Seat,data=davisdata)
```  
 
The boxplot shows that those who sit in the front dont drink too much while the people in the back drink heavily. Those that sit in the middle are between the two and drink a moderate amount. Meaning that those who sit in the back drink more than those in the middle or front. Over 75% of people who sit in the back drink more tan anyone sitting in the front and middle. 

### get fancy  
```{r}
basicCN <- ggplot(davisdata,aes(x=Seat,y=alcohol))

basicCN + geom_boxplot()
```
Those 
```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
The red dots are the outliers and the whiskers extend one and a half times the box. 
Using the data we can reject the null hypothesis. Based on the boxplots there is a clear difference in the amount that the back seats drink and those in the middle and front. 

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
The average number of drinks for the back row was 9.6, the middle was 3.2, and the front was 1.8. The average shows that the those in the back drank 3 times more than those in the middle and front. 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

We reject the null hypothesis, but we will seek clarification on which rows were different from other rows. 

```{r}
plot(TukeyHSD(model1))
```

Using the tukey boxplot we can tell that the front is different from the back and the middle is different from the back. however there is no difference between the middle and the front. 

## Conclusions

We began the assignment with doing a variable analysis which led to looking at the variables given in order to help identify what helper file was needed. After looking at the variables we needed the numerical~cat file which helped us with the problem. After analyzing the numerical~cat helper file we were able to past the commands after changing the variables within each command. After analyzing the results and data I concluded that I rejected the null hypothesis which means that there is a great difference between the amount that the back drinks compared to the front and middle rows.
